Computing Exact Restricted Isometry Constants via Mixed Integer Semidefinite Programming

### 2016-03-18 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
included number of instances used to compute average in results table

In Table~\ref{lhsRhsGap} we compare the relative gap between the bounds on $\alpha_k$ and $\beta_k$ produced by the two heuristics
and the exact values given by~\eqref{MISDP}, computed as their difference divided by the exact value. We present arithmetic means over all of the nine matrices for the given type that
could be solved within the time- and memory-limit. Note that we omitted the rank one matrices for the left-hand side since these satisfy
$\alpha_k = 0$ in all cases, so that the trivial lower bound would already be optimal.

>>>>

In Table~\ref{lhsRhsGap} we compare the relative gap between the bounds on $\alpha_k$ and $\beta_k$ produced by the two heuristics
and the exact values given by~\eqref{MISDP}, computed as their difference divided by the exact value. We present arithmetic means over all of the nine matrices for the given type that
could be solved within the time- and memory-limit. Note that for the left-hand side we also omitted all instances with $\alpha_k=0$, 
since we cannot compute a relative gap in that case. This included all rank one matrices. The number of instances used to compute the
average is given in brackets.
